Analysis and results

### 2020-09-10 analysis/03_analysis.Rmd

```{r load-data-output, warning=FALSE, message=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 1                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Thetas
draws_theta <- fit %>% 
  extract(
    pars = str_c("Theta[", 1:13, ",1]"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_theta %>% 
  mcmc_hist_by_chain()

draws_theta %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# Extract the L_Omega parameters only and look at trace plots, etc.

# L_Omega
draws_L_Omega <- fit %>% 
  extract(
    regex_pars = c("L_Omega"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_theta %>% 
  mcmc_hist_by_chain()

draws_theta %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

@@

# Check trace plots (SUBSET?)
color_scheme_set("mix-blue-red")
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    pars = str_c("Theta[", 1:13, ",1]"),
    n_warmup = 2000,
    facet_args = list(
      nrow = 2, 
      labeller = label_parsed
    )
  )

@@

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

@@

# Plot marginals
# if (intercept == 1) {
#   draws %>% 
#     mutate(
#       levels = factor(i, labels = level_labels)
#     ) %>%
#     ggplot(aes(x = Theta, y = levels)) + 
#     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#     # geom_halfeyeh(.width = .95) +
#     geom_vline(xintercept = 0, color = "grey") +
#     labs(y = "Attribute Levels")
# }

# if (intercept != 1) {
#   draws %>% 
#     filter(j != 1) %>% 
#     mutate(
#       levels = factor(i, labels = level_labels), 
#       covariates = factor(j, labels = covariate_labels)  
#     ) %>%
#     ggplot(aes(x = Theta, y = covariates)) +
#        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#        # geom_halfeyeh(.width = .95) +
#        geom_vline(xintercept = 0, color = "white") +
#        labs(y = "Covariates") +
#        facet_wrap(~ levels, ncol = 5)
# }

@@

if (intercept != 1) {
  # Posterior means.
  posterior_means <- draws %>% 
    filter(j != 1) %>% 
    left_join(j_labels, by = "j") %>% 
    left_join(level_lookup, by = "i") %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      # covariates = factor(j, labels = covariate_labels)
      covariates = factor(j, labels = 1:length(covariate_labels))
    ) %>% 
    group_by(category, attribute, j_label) %>% 
    summarize(
      mean = mean(Theta),
      ci_lower = quantile(Theta, .025),
      ci_upper = quantile(Theta, .975),
      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
    )

  # Heatmap of Theta matrix.
  plot_heatmap <- posterior_means %>% 
    mutate(
      gt_lt_zero = gt_zero + lt_zero,
      Coefficients = factor(
        gt_lt_zero, 
        levels = -1:1,
        labels = c("Negative", "Not Significant", "Positive"))
    ) %>% 
    ggplot(aes(x = j_label, y = attribute, fill = Coefficients)) +
    geom_tile(color = "white", size = 0.25) +
    # scale_fill_brewer(palette = "Blues") +
    scale_fill_manual(values = c(clrs$orange, "grey80", clrs$olive)) +
    scale_x_discrete(expand = c(0.001, 0.001)) +
    scale_y_discrete(expand = c(0.001, 0.001)) +
    # guides(fill = guide_legend(override.aes = list(key.height = 0.5, key.width = 0.5))) +
    guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
    theme_ngo(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom",
          strip.placement = "outside") +
    labs(
      title = plot_title,
      x = "Covariates",
      y = "Attribute Levels"
    ) + 
    # facet_wrap(~ category, ncol = 1, scales = "free_y")
    facet_grid(vars(category), scales = "free_y", space = "free_y")
}

>>>>

```{r load-data-output, warning=FALSE, message=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 1 # + Demographics

@@

# Gamma
draws_gamma <- fit %>% 
  extract(
    pars = str_c("Gamma[", 1:13, ",1]"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_gamma %>% 
  mcmc_hist_by_chain()

draws_gamma %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# Extract the Omega parameters only and look at trace plots, etc.

# Omega
draws_Omega <- fit %>% 
  extract(
    regex_pars = c("Omega"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_gamma %>% 
  mcmc_hist_by_chain()

draws_gamma %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

@@

# Check trace plots (SUBSET?)
color_scheme_set("mix-blue-red")
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    pars = str_c("Gamma[", 1:13, ",1]"),
    n_warmup = 2000,
    facet_args = list(
      nrow = 2, 
      labeller = label_parsed
    )
  )

@@

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Gamma[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

@@

# Plot marginals
# if (intercept == 1) {
#   draws %>% 
#     mutate(
#       levels = factor(i, labels = level_labels)
#     ) %>%
#     ggplot(aes(x = Gamma, y = levels)) + 
#     geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#     # geom_halfeyeh(.width = .95) +
#     geom_vline(xintercept = 0, color = "grey") +
#     labs(y = "Attribute Levels")
# }

# if (intercept != 1) {
#   draws %>% 
#     filter(j != 1) %>% 
#     mutate(
#       levels = factor(i, labels = level_labels), 
#       covariates = factor(j, labels = covariate_labels)  
#     ) %>%
#     ggplot(aes(x = Gamma, y = covariates)) +
#        geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
#        # geom_halfeyeh(.width = .95) +
#        geom_vline(xintercept = 0, color = "white") +
#        labs(y = "Covariates") +
#        facet_wrap(~ levels, ncol = 5)
# }

@@

if (intercept != 1) {
  # Posterior means.
  posterior_means <- draws %>% 
    filter(j != 1) %>% 
    left_join(j_labels, by = "j") %>% 
    left_join(level_lookup, by = "i") %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      # covariates = factor(j, labels = covariate_labels)
      covariates = factor(j, labels = 1:length(covariate_labels))
    ) %>% 
    group_by(category, attribute, j_label) %>% 
    summarize(
      mean = mean(Gamma),
      ci_lower = quantile(Gamma, .025),
      ci_upper = quantile(Gamma, .975),
      gt_zero = if_else(ci_lower > 0 & ci_upper > 0, 1, 0),
      lt_zero = if_else(ci_lower < 0 & ci_upper < 0, -1, 0)
    )

  # Heatmap of Gamma matrix.
  plot_heatmap <- posterior_means %>% 
    mutate(
      gt_lt_zero = gt_zero + lt_zero,
      Coefficients = factor(
        gt_lt_zero, 
        levels = -1:1,
        labels = c("Negative", "Not Significant", "Positive"))
    ) %>% 
    ggplot(aes(x = j_label, y = attribute, fill = Coefficients)) +
    geom_tile(color = "white", size = 0.25) +
    # scale_fill_brewer(palette = "Blues") +
    scale_fill_manual(values = c(clrs$orange, "grey80", clrs$olive)) +
    scale_x_discrete(expand = c(0.001, 0.001)) +
    scale_y_discrete(expand = c(0.001, 0.001)) +
    # guides(fill = guide_legend(override.aes = list(key.height = 0.5, key.width = 0.5))) +
    guides(fill = guide_legend(keywidth = 0.5, keyheight = 0.5)) +
    theme_ngo(base_size = 14) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "bottom",
          strip.placement = "outside") +
    labs(
      title = plot_title,
      x = "Covariates",
      y = "Attribute Levels"
    ) + 
    # facet_wrap(~ category, ncol = 1, scales = "free_y")
    facet_grid(vars(category), scales = "free_y", space = "free_y")
}
